Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-08-05 Masterarbeit_Robotik_Pamuk.tex
Remove from to include and add to rt performance tuning

@@

@@

\chapter{KVM exit reasons}\label{cha:kvm_exit_reasons}
\section{APIC\_WRITE}
\section{HLT}
\section{EPT\_MISCONFIG}
\section{PREEMPTION\_TIMER}
\section{EXTERNAL\_INTERRUPT}
\section{IO\_INSTRUCTION}
\section{EOI\_INDUCED}
\section{EPT\_VIOLATION}
\section{PAUSE\_INSTRUCTION}
\section{CPUID}
\section{MSR\_READ}

\chapter{To Include}\label{cha:to_include}
``korrekt''

@@

Vorgehensweise von~\cite{linPerformanceEvaluationXenomai}
\section{else}
Figure~\ref{fig:max_latency_vapic} shows latency of QEMU vapic Salamander4.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\columnwidth]{img/max_latency_vapic.png}
	\caption[Latency vapic]{Latency vapic}
	\label{fig:max_latency_vapic}
\end{figure}

@@

Figure~\ref{fig:max_latency_taskset} shows latency of QEMU taskset Salamander4.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\columnwidth]{img/max_latency_taskset.png}
	\caption[Latency taskset]{Latency taskset}
	\label{fig:max_latency_taskset}
\end{figure}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{|l|p{0.62\textwidth}|}
		\hline
		\textbf{Exit Reason} & \textbf{Description}                                     \\
		\hline
		APIC\_WRITE          & Triggered when the guest writes to its APIC.             \\ \hline
		EXTERNAL\_INTERRUPT  & Triggered by external hardware interrupts.               \\ \hline
		HLT                  & Triggered when the guest executes the HLT instruction.   \\ \hline
		EPT\_MISCONFIG       & Triggered by a misconfiguration in the EPT.              \\ \hline
		PREEMPTION\_TIMER    & Triggered when the host's preemption timer expires.      \\ \hline
		PAUSE\_INSTRUCTION   & Triggered when the PAUSE instruction is executed.        \\ \hline
		EPT\_VIOLATION       & Triggered by a violation of the EPT permission settings. \\ \hline
		IO\_INSTRUCTION      & Triggered when the guest executes an I/O instruction.    \\ \hline
		EOI\_INDUCED         & Triggered when an EOI signal is sent to the APIC.        \\ \hline
		MSR\_READ            & Triggered when the guest reads from a MSR.               \\ \hline
		CPUID                & Triggered when the guest executes the CPUID instruction. \\ \hline
	\end{tabular}
	\caption{Description of kvm\_exit reasons}
	\label{tab:kvm_exit}
\end{table}

@@

\begin{table}[H]
	\centering
	\begin{minipage}{.5\textwidth}
	\centering
	\caption{Host report CPU19 (Total of 445.908)}
	\label{tab:results_host_report}
	\begin{tabular}{|c|c|c|}
	\hline
	PID & Task & Count \\ \hline
	182579 & qemu-system-x86 & 302.748 \\ \hline
	0 & \textless{}idle\textgreater{} & 112.911 \\ \hline
	182618 & vhost & 21.204 \\ \hline
	182572 & qemu-system-x86 & 7.597 \\ \hline
	182755 & qemu-system-x86 & 644 \\ \hline
	182754 & qemu-system-x86 & 643 \\ \hline
	181870 & kworker/19:1 & 139 \\ \hline
	3820 & kworker/19:1H & 16 \\ \hline
	94 & migration/19 & 6 \\ \hline
	\end{tabular}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
	\centering
	\caption{Guest report (Total of 362.370)}
	\label{tab:results_guest_report}
	\begin{tabular}{|c|c|c|}
	\hline
	PID & Task & Count \\ \hline
	0 & \textless{}idle\textgreater{} & 150.744 \\ \hline
	331 & LRT-Main & 56.697 \\ \hline
	377 & trace-cmd & 48.507 \\ \hline
	346 & CLI & 26.426 \\ \hline
	378 & kthreadd & 25.837 \\ \hline
	340 & MainTaskLow & 19.291 \\ \hline
	339 & \textless{}...\textgreater{} & 9.980 \\ \hline
	34 & MainTaskHigh & 9.185 \\ \hline
	327 & LE-Logger & 4.965 \\ \hline
	369 & kworker/0:0 & 2.793 \\ \hline
	321 & kWorker-LRT & 2.542 \\ \hline
	328 & LRTMgr-Main & 1.651 \\ \hline
	34 & LrtMgrCyclic & 1.220 \\ \hline
	332 & cobalt\_printf & 1.112 \\ \hline
	325 & LE-System & 534 \\ \hline
	343 & TCP-Listen & 187 \\ \hline
	15 & rcu\_preempt & 162 \\ \hline
	25 & kcompactd0 & 122 \\ \hline
	58 & kworker/0:1H & 96 \\ \hline
	63 & kworker/u2:2 & 89 \\ \hline
	8 & jbd2/sda-8 & 86 \\ \hline
	22 & kworker/0:1 & 56 \\ \hline
	1 & init & 31 \\ \hline
	2 & kthreadd & 25 \\ \hline
	375 & trace-cmd & 24 \\ \hline
	14 & ksoftirqd/0 & 8 \\ \hline
	\end{tabular}
	\end{minipage}
	\end{table}

@@

\begin{table}[H]
	\centering
	\begin{tabular}{|p{0.1\textwidth}|p{0.45\textwidth}|p{0.45\textwidth}|}
	\hline
	\textbf{Number} & \textbf{Book} & \textbf{Citation} \\
	\hline
	\cite{maPerformanceTuningKVMbased} & Performance Tuning Towards a KVM-based Embedded Real-Time Virtualization System & It means that all threads, except for some per-core kernel threads, were prevented from running on the second processor core. \\
	\hline
	\cite{maPerformanceTuningKVMbased} & Performance Tuning Towards a KVM-based Embedded Real-Time Virtualization System & It means that all threads, except for some per-core kernel threads, were prevented from running on the second processor core. \\
	\hline
	\cite{maPerformanceTuningKVMbased} & Performance Tuning Towards a KVM-based Embedded Real-Time Virtualization System & It means that all threads, except for some per-core kernel threads, were prevented from running on the second processor core. \\
	\hline
	\cite{maPerformanceTuningKVMbased} & Performance Tuning Towards a KVM-based Embedded Real-Time Virtualization System & It means that all threads, except for some per-core kernel threads, were prevented from running on the second processor core. \\
	\hline
	\end{tabular}
	\caption{Your Caption}
	\label{tab:my_label}
	\end{table}

	Figure~\ref{fig:power_saver_kvm_exit} shows ...

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{img/power_saver/kvm_exit_count.png}
		\caption[power\_saver kvm\_exit\_count]{power\_saver kvm\_exit\_count}
		\label{fig:power_saver_kvm_exit}
	\end{figure}
	\clearpage

	Figure~\ref{fig:power_saver_kvm_host} shows ...

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{img/power_saver/results_host_report.png}
		\caption[power\_saver host report]{power\_saver host report}
		\label{fig:power_saver_kvm_host}
	\end{figure}
	\clearpage

	Figure~\ref{fig:power_saver_kvm_guest} shows ...

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{img/power_saver/results_guest_report.png}
		\caption[power\_saver guest report]{power\_saver guest report}
		\label{fig:power_saver_kvm_guest}
	\end{figure}
	\clearpage

	Figure~\ref{fig:balanced_kvm_exit} shows ...

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{img/balanced/kvm_exit_count.png}
		\caption[balanced kvm\_exit\_count]{balanced kvm\_exit\_count}
		\label{fig:balanced_kvm_exit}
	\end{figure}
	\clearpage

	Figure~\ref{fig:balanced_kvm_host} shows ...

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{img/balanced/results_host_report.png}
		\caption[balanced host report]{balanced host report}
		\label{fig:balanced_kvm_host}
	\end{figure}
	\clearpage

	Figure~\ref{fig:balanced_kvm_guest} shows ...

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{img/balanced/results_guest_report.png}
		\caption[balanced guest report]{balanced guest report}
		\label{fig:balanced_kvm_guest}
	\end{figure}
	\clearpage

	Figure~\ref{fig:performance_kvm_exit} shows ...

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{img/performance/kvm_exit_count.png}
		\caption[performance \_exit\_count]{performance \_exit\_count}
		\label{fig:performance_kvm_exit}
	\end{figure}
	\clearpage

	Figure~\ref{fig:performance_kvm_host} shows ...

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{img/performance/results_host_report.png}
		\caption[performance host report]{performance host report}
		\label{fig:performance_kvm_host}
	\end{figure}
	\clearpage

	Figure~\ref{fig:performance_kvm_guest} shows ...

	\begin{figure}[H]
		\centering
		\includegraphics[width=1.0\columnwidth]{img/performance/results_guest_report.png}
		\caption[balanced guest report]{balanced guest report}
		\label{fig:performance_kvm_guest}
	\end{figure}
	\clearpage

@@

	Figure~\ref{fig:gnuplot_max_latency_default}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.8\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/1default/gnuplot_max_latency_default.png}
		\caption[gnuplot latency no taskset]{gnuplot latency no taskset}
		\label{fig:gnuplot_max_latency_default}
	\end{figure}

	Figure~\ref{fig:gnuplot_max_latency_taskset}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.8\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/2taskset/gnuplot_max_latency_taskset.png}
		\caption[gnuplot latency with taskset]{gnuplot latency with taskset}
		\label{fig:gnuplot_max_latency_taskset}
	\end{figure}

	Figure~\ref{fig:gnuplot_max_latency_vapic}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.8\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/vapic/gnuplot_max_latency_vapic.png}
		\caption[gnuplot latency with taskset]{gnuplot latency with taskset}
		\label{fig:gnuplot_max_latency_vapic}
	\end{figure}

@@

	The Advanced Programmable Interrupt Controller (APIC) is responsible for the distribution of interrupts in x86 and Itanium-based computer systems. An APIC\_WRITE occurs when a guest operating system attempts to write to the APIC registers. Since the APIC is a physical hardware component, KVM must intercept this operation and cause a VM exit. To avoid this, newer Intel processors offer hardware virtualization of the Advanced Programmable Interrupt Controller (APICv). APICv improves virtualized AMD64 and Intel 64 guest performance by allowing the guest to directly access the APIC, dramatically cutting down interrupt latencies and the number of virtual machine exits caused by the APIC. This feature is used by default in newer Intel processors and improves I/O performance.

This can be done by setting the apic flag to 'v' in the VM configuration file.

Figure~\ref{fig:kvm_exit_vapic} shows ~\texttt{kvm\_exit} frequency with APIC virtualization. Comparing this to the previous Figures~\ref{fig:kvm_exit_taskset} and~\ref{fig:kvm_exits_default}, it can be observed that an APIC\_Write no longer occurs.

\begin{figure}[H]
	\centering
	\includegraphics[width=1.0\columnwidth]{img/kvm_exit_vapic.png}
	\caption[kvm exits default]{kvm exits default}
	\label{fig:kvm_exit_vapic}
\end{figure}

\chapter{Results}\label{cha:results}
~\cite{pixelartSIGMATEKKompletteAutomatisierungssysteme}
~\cite{Tracecmd}
~\cite{KernelShark}
~\cite{XenomaiXenomai}
~\cite{CPUEinheitenSIGMATEK}
~\cite{EngineeringToolLASAL}
~\cite{WelcomeYoctoProject}
~\cite{QEMU}
~\cite{maPerformanceTuningKVMbased}
~\cite{LinuxProcessPriorities}
~\cite{kernelrecipesKernelRecipes20162016}
~\cite{thelinuxfoundationFindingSourcesLatency2020}
~\cite{thelinuxfoundationChecklistWritingLinux2020}
~\cite{HOWTOBuildRTapplication}
~\cite{RealtimeProgrammingLinux}
~\cite{KVMQemuVirtualization}
~\cite{RealTimePerformanceTuning2022}
~\cite{MG996RServoMotor}
~\cite{DigitalOutputSIGMATEK}
~\cite{SDIASSIGMATEK}
~\cite{ControlsHMIsSIGMATEK}
~\cite{InterfacesSplittersSIGMATEK}
~\cite{adamPerformanceAssessmentLinux2021}
~\cite{adamRealTimePerformanceResponse2021}
~\cite{broskyShieldedProcessorsGuaranteeing2003}
~\cite{cinqueVirtualizingMixedCriticalitySystems2022}
~\cite{deoliveiraDemystifyingRealTimeLinux}
~\cite{garcia-vallsChallengesRealtimeVirtualization2014}
~\cite{guStateoftheArtSurveyRealTime2012}
~\cite{HardRealTime}
~\cite{javierperezHowRealTime2022}
~\cite{kirovaImpactModernVirtualization2019}
~\cite{kiszkaLinuxRealTimeHypervisor}
~\cite{huang2015performance}
~\cite{lutsykPipelinedMulticoreMachine2020}
~\cite{malallahComprehensiveStudyKernel2021}
~\cite{masrurVMBasedRealTimeServices2010}
~\cite{mckenneyRealTimeVs}
~\cite{pielAsymmetricSchedulingLoad2006}
~\cite{queirozTestingLimitsGeneralpurpose2023}
~\cite{reghenzaniRealTimeLinuxKernel2020}
~\cite{yoonRealTimePerformanceAnalysis}
~\cite{CPUUnitsSIGMATEK}
\clearpage

VARAN-Bus PCV-521\newline
Windows\newline
Ubuntu\newline
WSL\newline\newline\newline

In Xenomai 3, you need:

The Linux kernel with the Dovetail interface, which allows the kernel to handle real-time tasks with low latency.
The Cobalt real-time core, which is responsible for scheduling and executing real-time tasks.
In Xenomai 4, you need:
The Linux kernel with the EVL interface, which, like Dovetail, enables the kernel to handle real-time tasks with low latency.
The libevl library, which provides a user interface to the EVL core, allowing applications to use the real-time capabilities provided by EVL.
So, while both versions require a Linux kernel with a real-time interface (Dovetail for Xenomai 3, EVL for Xenomai 4), Xenomai 3 uses a real-time core (Cobalt), while Xenomai 4 uses a library (libevl) to provide applications with access to its real-time capabilities.
\end{comment}
\clearpage

>>>>

\bigskip \noindent It is important to mention that a real-time system implies determinism at every component of the system ranging from hardware over the kernel to the software and the application on it. As already established earlier, the guest OS Salamamder 4 runs Xenomai and is hence real-time capable. The host system also needs to be aware of the real-time determinism in order to achieve highest possible reliability. The very step of achieving the goal of reducing latency is to apply the preempt-rt patch \cite{RealtimePreempt_rt_versionsWiki} to the host system. This patch is a set of modifications to the Linux kernel with the goal of making it fully preemptible. This means, almost all parts of the kernel can be preempted and higher-priority tasks can interrupt lower-priority ones. This significantly reduces the time it takes for high-priority tasks to start executing after an event \cite{RealtimeKernelPatchset}. The patch also includes support for high-resolution timers and make the system more predictable, which are crucial for real-time applications where the timing of operations must be guaranteed with precise timing and scheduling \cite{rostedtInternalsRTPatch}.

\bigskip \noindent Nevertheless, a real-time kernel alone does not make a system truly “real-time” \cite{WhatRealtimeLinux}. Additional modifications are required to achieve this. After each tuning, the latency test of Xenomai will be executed to evaluate the improved latency of the system.

@@

After the BIOS configurations,

@@

\begin{comment}
\chapter{To Include}\label{cha:to_include}
``korrekt''

@@

Vorgehensweise von~\cite{linPerformanceEvaluationXenomai}
\section{Latency vapic}
Figure~\ref{fig:max_latency_vapic} shows latency of QEMU vapic Salamander4.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\columnwidth]{img/max_latency_vapic.png}
	\caption[Latency vapic]{Latency vapic}
	\label{fig:max_latency_vapic}
\end{figure}

@@

\section{Latency taskset}
Figure~\ref{fig:max_latency_taskset} shows latency of QEMU taskset Salamander4.
\begin{figure}[H]
	\centering
	\includegraphics[width=0.75\columnwidth]{img/max_latency_taskset.png}
	\caption[Latency taskset]{Latency taskset}
	\label{fig:max_latency_taskset}
\end{figure}

@@

\section{kvm exits}
\begin{table}[H]
	\centering
	\begin{tabular}{|l|p{0.62\textwidth}|}
		\hline
		\textbf{Exit Reason} & \textbf{Description}                                     \\
		\hline
		APIC\_WRITE          & Triggered when the guest writes to its APIC.             \\ \hline
		EXTERNAL\_INTERRUPT  & Triggered by external hardware interrupts.               \\ \hline
		HLT                  & Triggered when the guest executes the HLT instruction.   \\ \hline
		EPT\_MISCONFIG       & Triggered by a misconfiguration in the EPT.              \\ \hline
		PREEMPTION\_TIMER    & Triggered when the host's preemption timer expires.      \\ \hline
		PAUSE\_INSTRUCTION   & Triggered when the PAUSE instruction is executed.        \\ \hline
		EPT\_VIOLATION       & Triggered by a violation of the EPT permission settings. \\ \hline
		IO\_INSTRUCTION      & Triggered when the guest executes an I/O instruction.    \\ \hline
		EOI\_INDUCED         & Triggered when an EOI signal is sent to the APIC.        \\ \hline
		MSR\_READ            & Triggered when the guest reads from a MSR.               \\ \hline
		CPUID                & Triggered when the guest executes the CPUID instruction. \\ \hline
	\end{tabular}
	\caption{Description of kvm\_exit reasons}
	\label{tab:kvm_exit}
\end{table}

@@

\section{Host and Guest tasks}
\begin{table}[H]
	\centering
	\begin{minipage}{.5\textwidth}
	\centering
	\caption{Host report CPU19 (Total of 445.908)}
	\label{tab:results_host_report}
	\begin{tabular}{|c|c|c|}
	\hline
	PID & Task & Count \\ \hline
	182579 & qemu-system-x86 & 302.748 \\ \hline
	0 & \textless{}idle\textgreater{} & 112.911 \\ \hline
	182618 & vhost & 21.204 \\ \hline
	182572 & qemu-system-x86 & 7.597 \\ \hline
	182755 & qemu-system-x86 & 644 \\ \hline
	182754 & qemu-system-x86 & 643 \\ \hline
	181870 & kworker/19:1 & 139 \\ \hline
	3820 & kworker/19:1H & 16 \\ \hline
	94 & migration/19 & 6 \\ \hline
	\end{tabular}
	\end{minipage}%
	\begin{minipage}{.5\textwidth}
	\centering
	\caption{Guest report (Total of 362.370)}
	\label{tab:results_guest_report}
	\begin{tabular}{|c|c|c|}
	\hline
	PID & Task & Count \\ \hline
	0 & \textless{}idle\textgreater{} & 150.744 \\ \hline
	331 & LRT-Main & 56.697 \\ \hline
	377 & trace-cmd & 48.507 \\ \hline
	346 & CLI & 26.426 \\ \hline
	378 & kthreadd & 25.837 \\ \hline
	340 & MainTaskLow & 19.291 \\ \hline
	339 & \textless{}...\textgreater{} & 9.980 \\ \hline
	34 & MainTaskHigh & 9.185 \\ \hline
	327 & LE-Logger & 4.965 \\ \hline
	369 & kworker/0:0 & 2.793 \\ \hline
	321 & kWorker-LRT & 2.542 \\ \hline
	328 & LRTMgr-Main & 1.651 \\ \hline
	34 & LrtMgrCyclic & 1.220 \\ \hline
	332 & cobalt\_printf & 1.112 \\ \hline
	325 & LE-System & 534 \\ \hline
	343 & TCP-Listen & 187 \\ \hline
	15 & rcu\_preempt & 162 \\ \hline
	25 & kcompactd0 & 122 \\ \hline
	58 & kworker/0:1H & 96 \\ \hline
	63 & kworker/u2:2 & 89 \\ \hline
	8 & jbd2/sda-8 & 86 \\ \hline
	22 & kworker/0:1 & 56 \\ \hline
	1 & init & 31 \\ \hline
	2 & kthreadd & 25 \\ \hline
	375 & trace-cmd & 24 \\ \hline
	14 & ksoftirqd/0 & 8 \\ \hline
	\end{tabular}
	\end{minipage}
	\end{table}

@@

\section{Citation table}
\begin{table}[H]
	\centering
	\begin{tabular}{|p{0.1\textwidth}|p{0.45\textwidth}|p{0.45\textwidth}|}
	\hline
	\textbf{Number} & \textbf{Book} & \textbf{Citation} \\
	\hline
	\cite{maPerformanceTuningKVMbased} & book & citation \\
	\hline
	\cite{maPerformanceTuningKVMbased} & book & citation \\
	\hline
	\cite{maPerformanceTuningKVMbased} & book & citation \\
	\hline
	\cite{maPerformanceTuningKVMbased} & book & citation \\
	\hline
	\end{tabular}
	\caption{Your Caption}
	\label{tab:my_label}
	\end{table}

@@

\section{gnuplot latency with taskset}
	Figure~\ref{fig:gnuplot_max_latency_taskset}
	\begin{figure}[H]
		\centering
		\includegraphics[width=0.8\columnwidth]{masterthesis-documentation/docs/sigmatek/xenomai/2taskset/gnuplot_max_latency_taskset.png}
		\caption[gnuplot latency with taskset]{gnuplot latency with taskset}
		\label{fig:gnuplot_max_latency_taskset}
	\end{figure}

@@

\clearpage
\end{comment}
\chapter{Results}\label{cha:results}
~\cite{pixelartSIGMATEKKompletteAutomatisierungssysteme}
~\cite{Tracecmd}
~\cite{KernelShark}
~\cite{XenomaiXenomai}
~\cite{CPUEinheitenSIGMATEK}
~\cite{EngineeringToolLASAL}
~\cite{WelcomeYoctoProject}
~\cite{QEMU}
~\cite{RealtimePreempt_rt_versionsWiki}
~\cite{RealtimeKernelPatchset}
~\cite{rostedtInternalsRTPatch}
~\cite{WhatRealtimeLinux}
~\cite{maPerformanceTuningKVMbased}
~\cite{LinuxProcessPriorities}
~\cite{kernelrecipesKernelRecipes20162016}
~\cite{thelinuxfoundationFindingSourcesLatency2020}
~\cite{thelinuxfoundationChecklistWritingLinux2020}
~\cite{HOWTOBuildRTapplication}
~\cite{RealtimeProgrammingLinux}
~\cite{KVMQemuVirtualization}
~\cite{RealTimePerformanceTuning2022}
~\cite{MG996RServoMotor}
~\cite{DigitalOutputSIGMATEK}
~\cite{MG996RDigitalServo}
~\cite{SDIASSIGMATEK}
~\cite{ControlsHMIsSIGMATEK}
~\cite{InterfacesSplittersSIGMATEK}
~\cite{adamPerformanceAssessmentLinux2021}
~\cite{adamRealTimePerformanceResponse2021}
~\cite{broskyShieldedProcessorsGuaranteeing2003}
~\cite{cinqueVirtualizingMixedCriticalitySystems2022}
~\cite{deoliveiraDemystifyingRealTimeLinux}
~\cite{garcia-vallsChallengesRealtimeVirtualization2014}
~\cite{guStateoftheArtSurveyRealTime2012}
~\cite{HardRealTime}
~\cite{javierperezHowRealTime2022}
~\cite{kirovaImpactModernVirtualization2019}
~\cite{kiszkaLinuxRealTimeHypervisor}
~\cite{huang2015performance}
~\cite{lutsykPipelinedMulticoreMachine2020}
~\cite{malallahComprehensiveStudyKernel2021}
~\cite{masrurVMBasedRealTimeServices2010}
~\cite{mckenneyRealTimeVs}
~\cite{pielAsymmetricSchedulingLoad2006}
~\cite{queirozTestingLimitsGeneralpurpose2023}
~\cite{reghenzaniRealTimeLinuxKernel2020}
~\cite{yoonRealTimePerformanceAnalysis}
~\cite{CPUUnitsSIGMATEK}
\clearpage
